Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-06 Thesis/chapter/032-alt-theory-calculations.tex
write up SVM and KRR

@@

@@

\textbf{Support vector machines} often use the kernel method to ...

\begin{itemize}
    \item \sout{intro to stat and ml}
    \item \sout{say that although different will be abgehandelt in the same chapter}
    \item \sout{basic statistics: MAE vs MSE, R, std, F-test} 
    \item \sout{lin reg}
    \item \sout{ridge regression}
    \item kernel ridge regression 
    \item support vector machine 
    \item anova (categorical), PCA, step wise regression
    \item all previous ananlyse data to predict, but don't tell me which data point is needed next 
    \item DOE (add data acquisition)
    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimisation, actually incorporate prediction into selection process but don't per se specify which pred and optimisation)
    \item comment: always tradeoff between complexity and interpretability
    \item quesiton: which paragraph by GPT2?? 
\end{itemize}

>>>>

\td{mention classification vs regression and supervised vs supervised}

@@

\td{Note that when $\lambda$ tends to zero, the regularized loss function becomes the OLS loss function.
When $\lambda$ tends to infinity, we get an intercept-only model}
\td{A critique of ridge regression is that all the variables tend to end up in the model. The model only shrinks the coefficients.}
% from https://medium.com/@zxr.nju/the-classical-linear-regression-model-is-good-why-do-we-need-regularization-c89dba10c8eb

@@

\textbf{Support vector machines} 
\Gls{svm} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
\Gls{svm} is mainly used for classification, but can also be used for regression. 
Classifiction works by spanning a hyperplane between two categories in a way that the closest points from each category have the largest distance to the hyperplane. 
The distance from the points to the hyperplane is called margin.
These points are called support vectors and are used to define the hyperplane 
A \gls{svm} avoids overfitting by only using a subset - the support vectors - to fit the model. 
In the same manner as no data points are found within the margin for classification, 
no data points should be found outside of the margin. 
If the data is not seperable by a hyperplane the kernel trick can be used. 
The downside of \gls{svm} is that it is very

\begin{itemize}
    \item \sout{intro to stat and ml}
    \item \sout{say that although different will be abgehandelt in the same chapter}
    \item \sout{basic statistics: MAE vs MSE, R, std, F-test} 
    \item \sout{lin reg}
    \item \sout{ridge regression}
    \item \sout{kernel ridge regression}
    \item \sout{support vector machine}
    \item anova (categorical), PCA, step wise regression
    \item all previous ananlyse data to predict, but don't tell me which data point is needed next 
    \item DOE (add data acquisition)
    \item genetic algorithm and pso (they combine data gen with regression/prediction and optimisation, actually incorporate prediction into selection process but don't per se specify which pred and optimisation)
    \item comment: always tradeoff between complexity and interpretability
    \item quesiton: which paragraph by GPT2?? 
\end{itemize}
